---
title: "Preceptor Participation Suvery Results"
output: 
    html_notebook:
        code_folding: hide

---

```{r}
library(readr)
responses <- read_csv("responses.csv")
comments <- read_csv("comments.csv")
```

**Number of responses: `r length(unique(responses$responder))`**

### Which of the following do you feel are barriers to precepting resident research projects?

1. Disagree with processes of research subcommittee
1. Intimidated by degree of involvement
1. No perceived benefit for clinical ladder advancement
1. No protected work time for residency projects
1. No research ideas
1. Not interested in precepting projects

```{r message=FALSE}
library(dplyr)
library(stringr)
library(ggplot2)

ans <- c("Disagree with processes of research subcommittee" = "Research subcommittee",
         "Intimidated by degree of involvement" = "Intimidating",
         "No perceived benefit for clinical ladder advancement" = "Clinical ladder",
         "No protected work time for residency projects" = "No time",
         "No research ideas" = "No ideas",
         "Not interested in precepting projects" = "Not interested")

results <- filter(responses, question == 1) %>%
    mutate(score = (7 - rank) / 6,
           option = str_replace_all(option, ans)) %>%
    group_by(option) %>%
    summarize(score = sum(score)) %>%
    arrange(desc(score))
    
ggplot(results, aes(x = ordered(option, levels = results$option), y = score)) +
    geom_bar(stat = "identity", fill = "dark blue") +
    xlab("") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


### Are there any other barriers to precepting resident projects which were not listed?

### Which of the following do you feel are barriers to attending resident presentations?
